Mathematical Aspects of the Capital Market

### 2017-08-21 phd/MyThesis.tex
Updated the thesis manuscript.

\usepackage[numbers,sort&compress]{natbib}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{appendix}
\usepackage{multirow}
\graphicspath{
        {../papers/FX/}{../papers/Jeffrey1/}
        {../papers/Anja/}
        {../papers/DavisMikoschHeinyXie/}
}

@@

& Prof.~Olivier Wintenberger\\
& University of Marie \& Pierre Curie, Paris
\end{tabular}

@@

Furthermore, we study an importance sampling method for estimating
rare-event probabilities of multivariate heavy-tailed time series
generated by matrix recursion. We show that the proposed algorithm is
efficient in the sense that its relative error remains bounded as the
probability of interest tends to 0. We make use of exponential
twisting of the transition kernel of an {\em Markov additive process},
and take advantage of asymptotic theories on products of positive
random matrices.

\section*{Resum{\'e}}
Denne afhandling handler om analyse af tunge tailed tidsserier. Vi
diskuterer halen Egenskaber af real-world egenkapital retur serie og
undersøge mulighed for at et enkelt haleindeks deles af alle
returserier af aktivt handlede aktier i et marked. Betingelser for
denne hypotese til Være sande er identificeret.

Vi studerer egenværdier og egenvektorer af observerede kovarians og
observerede auto-kovarians matricer af multivariate heavy-tailed
tidsserier, og især til tidsserier med meget høje dimensioner.
Asymptotisk tilnærmelser af egenværdierne og egenvektorer af
sådanne matricer findes og udtrykkes i afhængighedens parametre
struktur, blandt andre.

Vi studerer også en importance samplings metod til estimering af
sjældne begivenheder sandsynligheder for multivariate heavy-tailed
tidsserier genereret af matrix recursion. Vi viser, at den foreslåede
algoritme er effektiv i den forstand, at dens relative fejl forbliver
afgrænset som sandsynligheden af interesse har tendens til 0. Vi gør
brug af eksponentiel vridning af overgangskernen til en {\em Markov
additive process} og tage fordel af asymptotiske teorier om produkter
af positiv tilfældig matricer.
\newpage
\section*{Acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}
I owe my gratitude to many people and especially to my supervisors
Prof. Thomas Mikosch and Prof. Jeffrey Collamore. Their insight and
guidance are indispensible throughout the scientific endeavor that
culminates in this thesis. Meanwhile, I cannot be more grateful to
Prof. Mogens Steffensen -- without his financial
support from the HIPERFIT program, my PhD project would not have
been feasible.

@@

To the professors and PhD students in the Mathematics department of
Copenhagen University and especially to Prof. Jostein Paulsen, I owe a
big ``thank you'' too. I really enjoyed working with him as a teaching
assistant and at the same time learned a lot of fantastic maths from him
and his book manuscript.

@@

Last but not least, I would like to thank the PhD committee for spending
their precious time to review and assess this thesis.
\bigskip

@@

\chapter*{Summary}
\addcontentsline{toc}{section}{Summary}
This PhD thesis provides results from analysis of heavy-tailed time
series. Its main part consists of the following research papers
written between October $2014$ and Augest $2017$.

@@

\bibitem[P3]{janssen:mikosch:rezapour:xie:2016:intro}
{\sc Janssen, A., Mikosch, T., Mohsen, R. and Xie, X.}
\newblock Limit theory for the singular values of the sample autocovariance
  matrix function of multivariate time series.
\newblock {\em Bernoulli, to appear}.

\bibitem[P4]{davis:mikosch:heiny:xie:20151}
{\sc Davis, R.~A., Heiny, J., Mikosch, T., and Xie, X.}
\newblock Extreme value analysis for the sample autocovariance matrices of
  heavy-tailed multivariate time series.
\newblock {\em Extremes 19}, 3 (2016), 517--547. \href{http://link.springer.com/article/10.1007/s10687-016-0251-7}{\blue{[pdf]}}
\end{enumerate}

>>>>

\usepackage[numbers,sort&compress]{natbib}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{appendix}
\usepackage{pstricks, pst-barcode}
\usepackage{multirow}
\graphicspath{
        {../papers/FX/}{../papers/Jeffrey1/}
        {../papers/Anja/}
        {../papers/DavisMikoschHeinyXie/}
}

@@

& Prof.~Olivier Wintenberger\\
& University Marie \& Pierre Curie, Paris
\end{tabular}

@@

Furthermore, we study an importance sampling method for estimating
rare-event probabilities of multivariate heavy-tailed time series
generated by matrix recursion. We show that the proposed algorithm is
efficient in the sense that its relative error remains bounded as the
probability of interest tends to zero. We make use of exponential
twisting of the transition kernel of an {\em Markov additive process},
and take advantage of asymptotic theories on products of positive
random matrices.

\section*{Resum{\'e}}
Denne afhandling handler om analyse af tidsrækker med tunge haler. Vi 
diskuterer haleegenskaber af real-world equity return serie og
undersøge muligheden for at et enkelt haleindeks deles af alle
return serier af aktivt handlede aktier i et marked. Betingelser for
denne hypotese til være sande er identificeret.

Vi studerer egenværdier og egenvektorer af observerede kovarians- og
auto-kovarians- matricer af multivariate tung-halede
tidsrækker, og især til tidsrækker med meget høje dimensioner.
Asymptotiske tilnærmelser af egenværdierne og egenvektorer af
sådanne matricer findes og udtrykkes i afhængighedens parameter
struktur, blandt andre.

Vi studerer også en importance sampling metode til estimering
sandsynligheder af sjældne begivenheder for multivariate tung-halede
tidsrækker genereret af matrice rekursioner. Vi viser, at den foreslåede
algoritme er effektiv i den forstand, at dens relative fejl forbliver
afgrænset som sandsynligheden af interesse har tendens til nul. Vi gør
brug af eksponentiel vridning af overgangskernen til en {\em Markov
additive process} og tage fordel af asymptotiske teorier om produkter
af positive tilfældige matricer.
\newpage
\section*{Acknowledgments}
\addcontentsline{toc}{section}{Acknowledgments}
I owe my gratitude to many people and especially to my supervisors
Prof. Thomas Mikosch and Prof. Jeffrey Collamore. Their insight and
guidance are indispensable throughout the scientific endeavor that
culminates in this thesis. Meanwhile, I cannot be more grateful to
Prof. Mogens Steffensen -- without his financial
support from the HIPERFIT program, my PhD project would not have
been feasible.

@@

To the professors and PhD students in the Mathematics Department of
Copenhagen University and especially to Prof. Jostein Paulsen, I owe a
big ``thank you'' too. I really enjoyed working with him as a teaching
assistant and at the same time learned a lot of fantastic maths from him
and his book manuscript.

@@

Last but not least, I would like to thank the PhD Committee for spending
their precious time to review and assess this thesis.
\bigskip

@@

\chapter*{Summary}
\addcontentsline{toc}{section}{Summary}
This PhD thesis provides results from analysis of heavy-tailed time
series. Its main part consists of the following research papers
written between October $2014$ and August $2017$.

@@

\bibitem[P3]{janssen:mikosch:rezapour:xie:2016:intro}
{\sc Janssen, A., Mikosch, T., Mohsen, R. and Xie, X.}
\newblock Limit theory for the singular values of the sample auto-covariance
  matrix function of multivariate time series.
\newblock {\em Bernoulli, to appear}.

\bibitem[P4]{davis:mikosch:heiny:xie:20151}
{\sc Davis, R.~A., Heiny, J., Mikosch, T., and Xie, X.}
\newblock Extreme value analysis for the sample auto-covariance matrices of
  heavy-tailed multivariate time series.
\newblock {\em Extremes 19}, 3 (2016), 517--547. \href{http://link.springer.com/article/10.1007/s10687-016-0251-7}{\blue{[pdf]}}
\end{enumerate}
